%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\usepackage{hyperref}


\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Nora Bradford } % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline {noraab@uci.edu} % Your address
\moveleft.5\hoffset\centerline {781-879-4708}

%----------------------------------------------------------------------------------------

\begin{resume}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

University of California, Irvine \hfill 2020-present \\
Ph.D., Cognitive Sciences \\
Concentration: Cognitive Neuroscience \\
Advisors: Dr. Megan Peters \& Dr. Barbara Sarnecka 

University of Pennsylvania \hfill 2019 \\
Post-Baccalaureate Student 

University of Chicago \hfill 2015-2019 \\
B.S. Neuroscience, B.A. Psychology, B.A. Philosophy (with Honors \& Dean's List) \\
Advisor: Dr. Leslie Kay \\
Thesis: Testing Piriform Cortex Inputs to Granule Cells as Modulators of Excitability Leading to Beta Oscillations
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}
{Marine Biological Laboratory, Woods Hole, MA} \hfill 2022 \\
{\sl Summer Science Writer}

{The Broad Institute, MIT \& Harvard} \hfill 2022 \\
{\sl Science Writing and Communications Intern}

{Digital Learning Lab, UC Irvine, Dr. Mark Warschauer} \hfill 2021 \\
{\sl Graduate Student Researcher}

{Communication Neuroscience Lab, UPenn, Dr. Emily Falk} \hfill 2020 \\
{\sl Research Associate}

{Developing Minds Lab, UPenn, Dr. Elizabeth Brannon} \hfill 2019-2020 \\
{\sl Lab Manager}


%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------
 
\section{AWARDS}
{Norman Weinberger Award from the Center for the Neurobiology}\hfill 2022\\
{of Learning and Memory, UC Irvine}\\
{\sl ``...will support an exceptional graduate student that embodies Professor Weinberger's high standards for doctoral trainees"}

{Graduate Division Inclusive Excellence Award}\hfill 2022

{Council for the Advancement of Science Writing Travel fellowship}\hfill 2021

{School of Social Sciences Award for Public Writing} \hfill 2021

{Graduate Innovation Fellowship, UCI Beall Applied Innovation} \hfill 2021-2022 \\
{\sl Marketing Communication - Marketing
Science, Data Flow, and Results \\Interpretation track}

{Science Communication Fellowship, NPR} \hfill 2020, 2021 \\
{\sl Loh Down On Science Podcast}

{Lawrence A. Kimpton Fellowship} \hfill 2019 

{BSCD-NSCI Summer Research Fellowship} \hfill 2018 

{Admissions Outreach Metcalf Fellowship} \hfill 2017 

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
 
\section{PUBLICATIONS and CONFERENCE PROCEEDINGS}
Xu, Y., Wang, D., Yu, M., Ritchie, D., Yao, B., Wu, T., Zhang, Z., Li, T., \textbf{Bradford N.}, Sun, B., Hoang, T., Sang, Y., Hou, Y., Ma, X., Yang, D., Peng, N., Yu, Z., Warschauer, M. (2022). Fantastic questions and where to find them: FairytaleQA— An authentic dataset for narrative comprehension. {\sl Association for Computational Linguistics}

Grasselli G., Boele H.J., Titley H., \textbf{Bradford N.}, van Beers L., Jay L., De Zeeuw C.I., Schonewille M., Hansel C. Learning deficit associated with a selective and cell-type specific impairment of intrinsic plasticity in cerebellar Purkinje cells.  {\sl PLoS Biology}

%----------------------------------------------------------------------------------------
%	PRESENTATIONS
%----------------------------------------------------------------------------------------
\section{TALKS}
\textbf{Bradford N.}, Peters, M. Effects of Perceived Numerosity on Confidence, Association for the Scientific Study of Consciousness Annual Meeting, Amsterdam, the Netherlands (July 12-14, 2022)

\section{POSTERS}
\textbf{Bradford N.}, Peters, M. Investigating Metacognitive Sensitivity in Online Learning Tool for Undergraduates, Neuromatch Conference, virtual (Dec 1-2, 2021)

\textbf{Bradford N}, Tao E, Nguyen V, Kay L. Testing Piriform Cortex inputs to Granule Cells as Modulators of Excitability leading to Beta Oscillations, Midwestern Psychological Association Annual Meeting, Chicago, IL (April 11-13, 2019)

Grasselli G (presenter), Boele HJ, Titley H, \textbf{Bradford N.}, van Beers L, Jay L, De Zeeuw CI, Schonewille M, Hansel C. Learning deficit associated with a selective and cell-type specific impairment of intrinsic plasticity in cerebellar Purkinje cells, Society for Neuroscience (SfN) annual meeting 2018, San Diego (CA, USA), (Nov 3-7) (oral presentation)

\textbf{Bradford N.}, Tao E., Nguyen V., Kay L. Testing Piriform Cortex inputs to Granule Cells as Modulators of Excitability leading to Beta Oscillations. Midstates Consortium for Math and Science Undergraduate Research Symposium on Biological Sciences and Psychology. Chicago, IL (November 2018) 

\textbf{Bradford N.}, Tao E., Nguyen V., Kay L. Testing Piriform Cortex inputs to Granule Cells as Modulators of Excitability leading to Beta Oscillations. 5th Annual University of Chicago Undergraduate Research Symposium. Chicago, IL (October 2018)


Bailey L., \textbf{Bradford N.}, Chigier S., Gustafson J., Iyer H., Liapin M., Sherrin M., Zhan B., Rokous J. Molecular Locomotion: Modeling the Functional Domains of E1 Helicase to Assess the Asymmetric Rotary Model of E1 Helicase. American Society for Biochemistry and Molecular Biology, Boston, MA, (March 2015)

\textbf{Bradford N.}, Cho Y.J., Bailey L., Gustafson J., Huang T., Iyer H., Lu H., Magliochetti-Cammarata T., Nee W., Park J., Park J.Y., Sherrin M., Sugarman E., Tejeda J., Zhan B., Rokous J. Using a Chimera to Study the Role of Galectin-1 in Immunological Responses and Tumor Progression. American Society for Biochemistry and Molecular Biology, San Diego, CA (March 2014)

Bang J., \textbf{Bradford N.}., Harrold E., Huang T., Lu H., Magliochetti-Cammarata T., Nee W., O'Dea C., Park J., Robinson I., Rokous J., Sugarman E., Tejeda J., Yan V., Rokous J. SMARTer design of a novel structure-based ADAM8 inhibitor to combat pancreatic cancer. American Society for Biochemistry and Molecular Biology, Boston, MA (March 2013)

%----------------------------------------------------------------------------------------
%	Other Writing
%----------------------------------------------------------------------------------------

\section{WRITING FOR GENERAL PUBLIC}
Bradford, N. (2022, Mar 3). \#WhyIScience Q\&A: Meet a research associate with a passion for perfecting research methods. In {\sl Broad Institute of MIT and Harvard}. \href{https://www.broadinstitute.org/blog/whyiscience-qa-meet-research-associate-passion-perfecting-research-methods}{Link}

Bradford, N. (2022, Mar 2). Repeated urinary tract infections may stem from a disrupted microbiome. In {\sl Broad Institute of MIT and Harvard}. \href{https://www.broadinstitute.org/news/repeated-urinary-tract-infections-may-stem-disrupted-microbiome}{Link}


Bradford, N. (2022, Apr 19). Study finds new patterns of antibiotic resistance spread in hospitals. In {\sl Broad Institute of MIT and Harvard}. \href{https://www.broadinstitute.org/news/study-finds-new-patterns-antibiotic-resistance-spread-hospitals}{Link}

Bradford, N. (2022, Mar 21). \#WhyIScience Q\&A: An aspiring physician-scientist investigates health through the eye
. In {\sl Broad Institute of MIT and Harvard}. \href{https://www.broadinstitute.org/blog/whyiscience-qa-aspiring-physician-scientist-investigates-health-through-eye}{Link}

Bradford, N. (2022, Mar 21). Making 100,000 whole genome sequences available. In {\sl Broad Institute of MIT and Harvard}. \href{https://www.broadinstitute.org/news/making-100000-whole-genome-sequences-available}{Link}


Bradford, N. (2022, Feb 22). Population-based study reveals strong genetic links with multiple cardiometabolic diseases and traits. In {\sl Broad Institute of MIT and Harvard}. \href{https://www.broadinstitute.org/news/population-based-study-reveals-strong-genetic-links-multiple-cardiometabolic-diseases-and-0}{Link}

Bradford, N. (2022, Feb 3). Researchers identify new target for treatment of aggressive childhood brain tumors. In {\sl Broad Institute of MIT and Harvard}. \href{https://www.broadinstitute.org/news/researchers-identify-new-target-treatment-aggressive-childhood-brain-tumors}{Link}

Bradford, N. (2022, Feb 2). \#WhyIScience Q\&A: A computer scientist builds data-protection tools and is raising awareness about cybersecurity. In {\sl Broad Institute of MIT and Harvard}. \href{https://www.broadinstitute.org/blog/whyiscience-qa-computer-scientist-builds-data-protection-tools-and-raising-awareness-about}{Link}

Bradford, N. (2021, Nov 22). Finding research inspiration in life experience. In {\sl UCI Social Science News}. \href{https://www.socsci.uci.edu/newsevents/news/2021/2021-11-22-zeinab-kachakeche.php}{Link}

Bradford, N. (2021, Nov 22). Bee Building Blocks [Audio podcast episode]. In {\sl Loh Down On Science}. NPR. \href{https://lohdownonscience.com/bee-building-blocks/}{Link}

Bradford, N. (2021, Nov 15). Ad-itude [Audio podcast episode]. In {\sl Loh Down On Science}. NPR. \href{https://lohdownonscience.com/ad-itude/}{Link}

Bradford, N. (2021, Oct 20). Woodland Growth [Audio podcast episode]. In {\sl Loh Down On Science}. NPR. \href{https://lohdownonscience.com/woodland-growth/}{Link}

Bradford, N. (2021, Oct 19). Novel brain research could feed misplaced sci-fi worries for the public. In {\sl CASW New Horizons Newsroom 2021}.\href{https://casw.org/news/novel-brain-research-could-feed-misplaced-sci-fi-worries-for-the-public/}{Link} 

Bradford, N. (2021, Oct 19). The changing landscape of science filmmaking. In {\sl NASW News}. \href{https://www.nasw.org/article/changing-landscape-science-filmmaking}{Link} 

Bradford, N. (2021, Oct 15). Research in Action. In {\sl UCI Social Science News}. \href{https://www.socsci.uci.edu/newsevents/news/2021/2021-10-15-gillooly.php}{Link} 

Bradford, N. (2021, Oct 5). Time Flies When You're in Lockdown. In {\sl NASW Student Newsroom}. \href{https://nasw.org/article/time-flies-when-youre-lockdown}{Link}

Bradford, N. (2021, Oct 5). Three Thumbs Up [Audio podcast episode]. In {\sl Loh Down On Science}. NPR. \href{https://lohdownonscience.com/three-thumbs-up/}{Link}

Bradford, N. (2021, Oct 5). UC Irvine researchers hope that teaching computing language to kids will help level the playing field. OC Registrar. \href{https://www.ocregister.com/2021/10/05/uc-irvine-researchers-hope-that-teaching-computing-language-to-kids-will-help-level-the-playing-field/}{Link}

Bradford, N. (2021, July 21). Speedy Sponges [Audio podcast episode]. In {\sl Loh Down On Science}. NPR. \href{https://lohdownonscience.com/speedy-sponges/}{Link}

Bradford, N. (2021, June 29). Slimey Memories [Audio podcast episode]. In {\sl Loh Down On Science}. NPR. \href{https://lohdownonscience.com/slimey-memories/}{Link}

Bradford, N. (2021, June 17). Fighting for fair housing. In {\sl UCI Social Science News}. \href{https://www.socsci.uci.edu/newsevents/news/2021/2021-06-17-schmidt-haynes-foundation.php}{Link}

Bradford, N. (2021, June 11). Future Thinking [Audio podcast episode]. In {\sl Loh Down On Science}. NPR. \href{https://lohdownonscience.com/future-thinking/}{Link} 

Bradford, N. (2021, May 11). Current Events [Audio podcast episode]. In {\sl Loh Down On Science}. NPR. \href{https://lohdownonscience.com/current-events/}{Link}

Bradford, N. (2021, April 28). Sooner or Laser [Audio podcast episode]. In {\sl Loh Down On Science}. NPR. \href{https://lohdownonscience.com/sooner-or-laser/}{Link}

Bradford, N. (2021, April 22). Fractal Beauty [Audio podcast episode]. In {\sl Loh Down On Science}. NPR. \href{https://lohdownonscience.com/fractal-beauty/}{Link}

Bradford, N. (2021, March 28). How local surfers can help scientists with ocean restoration. LA Daily News. \href{https://www.dailynews.com/2021/03/28/how-local-surfers-can-help-scientists-with-ocean-restoration/}{Link}

Bradford, N. (2021, March 28). Be a friend to Earth, save a fungus. LA Daily News. \href{https://www.dailynews.com/2021/03/28/be-a-friend-to-earth-save-a-fungus/}{Link}

Bradford, N. (2021, March 23). Cellular Time Travel [Audio podcast episode]. In {\sl Loh Down On Science}. NPR.  \href{https://lohdownonscience.com/cellular-time-travel/}{Link}

Bradford, N. (2021, February 25). Suction Saves The Day [Audio podcast episode]. In {\sl Loh Down On Science}. NPR.  \href{https://lohdownonscience.com/suction-saves-the-day/}{Link}

Bradford, N. (2021, February 1). SapQuest [Audio podcast episode]. In {\sl Loh Down On Science}. NPR.  \href{https://lohdownonscience.com/sapquest/}{Link}




%----------------------------------------------------------------------------------------
%	TEACHING
%---------------------------------------------------------------------------------------- 

\section{TEACHING}
Psych 7A Introduction to Psychology \\ 
{\sl Teaching Assistant} \hfill {March 2021 - June 2021}

Psych 140L Principles of Learning Theory \\ 
{\sl Teaching Assistant} \hfill {January 2021 - March 2021} 

Psych 169 Consciousness and the Brain \\
{\sl Teaching Assistant}\hfill {September 2020 - December 2020} 



%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%---------------------------------------------------------------------------------------- 
\section{PROFESSIONAL SERVICE}

{Diverse Educational Community and Doctoral Experience (DECADE)} \\
{\sl Department Representative}\hfill 2021-present

{NEURO Club, UChicago} \\
{\sl President}\hfill{2016-2019}

{Society for Neuroscience Undergraduates in Chicago} \\
{\sl Board Member}\hfill{2018-2019}

{Admissions Outreach Office, UChicago} \\
{\sl Outreach Intern Coordinator}\hfill{2016-2019}

{Elucidations Philosophy Podcast} \\
{\sl Intern}\hfill{2017-2019}


\section{COMMUNITY SERVICE}


{Minority Mentorship Program, Governor's Academy} \\
{\sl Organizer}\hfill 2020-present

{Farmers Market, The Food Trust} \\
{\sl Part-time Market Associate}\hfill 2019-present

{NEURO Mentorship Program} \\
{\sl Founder and Mentor}\hfill{2018-2019}

{Women in Science Mentorship Program} \\
{\sl Mentor}\hfill{2018-2019}

{Phoenix Biology Mentorship Program} \\
{\sl Mentor}\hfill{2017-2018}

{Maroon Tutor Match} \\
{\sl Tutor}\hfill{2017-2018}


%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------


\section{OTHER TRAINING} 
ComSciCon-SciWri Workshop \hfill 2021 \\
{\sl  Science Writers 2021 Conference}

Mentoring Excellence Program, UCI Graduate Division \hfill 2021 \\
{\sl  Mentoring Excellence Certificate}

Knight Science Journalism @ MIT \hfill 2021 \\
{\sl  Fact-Checking Workshop Certificate}

UCI as a Minority Thriving University \hfill 2021 \\
{\sl Inclusive Excellence Certificate}

Interactive Student, Computational Neuroscience Course\hfill 2020 \\
{\sl Neuromatch Academy}

MRI Technician Level II Training \hfill 2019 \\
{\sl University of Pennsylvania}


\end{resume}
\end{document}
